---
title: "Homework 5"
author: "Hemangi Modi"
date: "2022-11-15"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


## Problem 1

```{r}
full_df = 
  tibble(
    files = list.files("data/zip_data/"),
    path = str_c("data/zip_data/", files)
  ) %>% 
  mutate(data = map(path, read_csv)) %>% 
  unnest()
```

```{r}
tidy_df = 
  full_df %>% 
  mutate(
    files = str_replace(files, ".csv", ""),
    group = str_sub(files, 1, 3)) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>% 
  select(group, subj = files, week, outcome)
```

```{r}
tidy_df %>% 
  ggplot(aes(x = week, y = outcome, group = subj, color = group)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~group)
```

## Problem 2

```{r}
homicides_df = 
  read_csv("data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, ", ", state )
  )
```

### Describing the dataset
This dataset contains data on homicides in 50 large U.S cities. There are `r nrow(homicides_df)` observations and 12 columns. Some of the key variables include: the date the homicide was reported, information about the victim (first and last name, race, age, sex), the city, the state, and the state/disposition of the case (whether the case is open or closed and if an arrest was made). 


```{r}
summary_df =
  homicides_df %>% 
  group_by(city_state) %>% 
  summarize(
    total_count = n(),
    unsolved_count = sum((disposition == "Open/No arrest" | disposition == "Closed without arrest"))
  )
```

```{r}
balt_df = 
  summary_df %>% 
  filter(city_state == "Baltimore, MD")
  
prop_test_balt = 
  prop.test(x = balt_df %>% pull(unsolved_count), n = balt_df %>% pull(total_count)) %>% 
  broom::tidy() %>% 
  select(
    estimate, "CI_lower" = conf.low, "CI_higher" = conf.high
  )

prop_test_balt
```


```{r}
prop_each_city = 
  summary_df %>% 
  mutate(
    p_test = map2(unsolved_count, total_count, ~prop.test(.x, .y) %>% broom::tidy())
  ) %>% 
  unnest() %>% 
  select(
    city_state, estimate, "CI_lower" = conf.low, "CI_higher" = conf.high
  )

prop_each_city

```

```{r}
homicides_plot = 
  prop_each_city %>% 
  ggplot(aes(x = reorder(city_state, estimate), y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_higher)) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1))

homicides_plot
```


## Problem 3

```{r}
simulation_fx = function(mu, n = 30, sigma = 5) {
  simulation_df = 
    tibble(
      x = rnorm(n, mean = mu, sd = sigma)
    )

  simulation_df %>% 
    summarize (
      mu_hat = mean(x),
      p_value = broom::tidy(t.test(x))[[3]] 
    )

}
```

```{r}
simulation_results_df_0 = 
  expand_grid(
    mu = 0,
    iter = 1:5000
  ) %>% 
  mutate(
    estimates_df = map(mu, simulation_fx)
  ) %>% 
  unnest(estimates_df)
```

```{r}
sim_results_df_1_to_6 = 
  expand_grid(
    mu = c(1, 2, 3, 4, 5, 6),
    iter = 1:5000
  ) %>% 
  mutate(
    estimate_df_1_to_6 = map(mu, simulation_fx)
  ) %>% 
  unnest(estimate_df_1_to_6)
```

